---
title: "Spatial Figures Peer Review"
output: html_document
---
# PUT YOUR NAME HERE
Ruddy Setiadi Gunawan

## Problem 1

Create the following figure, using the data included in the R Markdown file.

```{r problem_1_data,include=FALSE}

library(tidyverse)
library(maps)

####make some data for painting the map

my_world_map <- map_data("world")

countries <- unique(my_world_map$region)

set.seed(987)
some_data_values <- data.frame(

  "region"=countries,
  
  "Score"=runif(252,0,100))

```

```{r problem_1,echo=FALSE,message=FALSE}

####Make sure you install any necessary libraries

####HINT: Use the following code to get the colors right
#scale_fill_distiller(palette=5)

####HINT: make sure you use left_join to combine the data_values above to the world map data in my_world_map

####PUT YOUR CODE HERE
merged_data <- left_join(my_world_map, some_data_values, by = c("region"="region"))

ggplot(data = merged_data, mapping = aes(x = long, y = lat, group = group, fill = Score)) +
  geom_polygon() +
  scale_fill_distiller(palette = "Greens", direction = -1, guide = "colorbar") +
  labs(title = "Problem 1")
```

## Problem 2

Create the following figure, using the data included in the R Markdown file.


```{r problem_2_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK
set.seed(15)
Measurement<-rnorm(32,50,1)
```


```{r solution_p2,echo=FALSE,message=FALSE}

####Make sure you load any necessary libraries

####HINT: Use a filter command to get just maps of Costa Rica, Panama, and Nicaragua

####Hint: Use a filter command to put in points only for cities with a population of greater than 40,000. This should leave you with 32 cities.

####Hint: Use add_column to attach the "Measurement" variable to your data, and set that to the color aesthetic when you draw the points.

####Hint: set the colors for the city points with scale_color_distiller(palette=7)

####Hint: set the size of all points to the value 5

####PUT YOUR CODE HERE
central_america <- merged_data %>%
  filter(region %in% c("Costa Rica", "Panama", "Nicaragua"))

my_cities <-maps::world.cities

central_america_cities <- my_cities %>%
  filter(country.etc %in% c("Costa Rica", "Panama", "Nicaragua") & pop > 40000)

central_america_cities <- central_america_cities %>%
  add_column(Measurement = Measurement)

ggplot(data = central_america, mapping = aes(x = long, y = lat, group = group)) +
    geom_polygon(color = "black", fill = "white") +
    geom_point(data = central_america_cities, aes(x = long, y = lat, group = NULL, color = Measurement), size = 5) +
    scale_color_distiller(palette=7, direction=-1, breaks=49:51, limits = c(49, 51)) + labs(title = "Problem 2")
```

## Problem 3

Create the following figure, using the data included in the R Markdown file.

Note that the code in the .rmd file will import a set of simple features data for South America. Make sure you install any necessary packages. 

```{r problem_3_data,include=FALSE}

#####INSTALL THESE PACKAGES IF NECESSARY
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)

####DO NOT MODIFY
s_america<-ne_countries(scale="medium",continent='south america',returnclass="sf")

```

```{r problem3,echo=FALSE}

####Make sure you load any necessary libraries

####HINT: the s_america object created in the chunk above is a simple features object with many columns. Identify the correct column based on the solution figure and use it to color in the choropleth.

####HINT: Use scale_fill_distiller and palette 10 to the match the colors.

####PUT YOUR CODE HERE
ggplot() +
    geom_sf(data = s_america, aes(fill = pop_est)) +
    scale_fill_distiller(palette=10, n.breaks = 5, direction=-1, guide=guide_colorbar()) +
    labs(title = "Problem 3") +
    scale_x_continuous(
        labels = function(x) sprintf("%.1f째W", -1 * x)
    ) +
    scale_y_continuous(
        labels = function(y) {
            ifelse(y < 0, sprintf("%.1f째S", -1 * y), ifelse(y == 0, "0째", sprintf("%.1f째N", y)))
        }
    ) +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, hjust = 1)
    )
```


